Performance Models for Data Transfers: A Case Study with Molecular Chemistry Kernels

### 2019-04-07 ICPP-19/communications.tex
minor
Changes after Lionel tikz diagrams:

\begin{algorithm}
	\caption{\label{alg:OrderOfExecutionInfinteMemory}Algorithm to determine the order of processing and schedule for a set of ready tasks (infinite memory case)}
	\begin{algorithmic}[1]
		\STATE Divide ready tasks in two sets $S_1$ and $S_2$. If computation time of a task $T$is not less than its communication time, then $T$ is in $S_1$ otherwise $S_2$.
		\STATE Sort $S_1$ in queue $Q$ by non-decreasing communication times
		\STATE Sort $S_2$ in queue $Q'$ by non-increasing computation times
		\STATE Append $Q'$ to $Q$
		\STATE $early\_available\_time\_on\_communication\_resource \gets 0$
		\STATE $early\_available\_time\_on\_computation\_resource \gets 0$
		\WHILE{$Q \neq \emptyset$}
		\STATE remove a task $T$ from beginning of $Q$ for processing
		\STATE $\scomm(T) \gets  early\_available\_time\_on\_communication\_resource$
		\STATE $\scomp(T) \gets  max(\scomm(T) + CM_T, early\_available\_time\_on\_computation\_resource)$
		\STATE $early\_available\_time\_on\_communication\_resource \gets  \scomm(T) + CM_T$
		\STATE $early\_available\_time\_on\_computation\_resource \gets  \scomp(T) + CP_T$
		\ENDWHILE
	\end{algorithmic}
\end{algorithm}

@@

	\begin{figure}[htb]
		\centering
		\includegraphics[scale=0.5]{Figs/first_segment}
		\caption{ \label{fig:firstSegment} First segment of Schedule $S$.}
	\end{figure}

@@

\begin{figure}[htb]
	\centering
	%% 	\subfloat[Optimal schedule]{
	\begin{tikzpicture}[decoration={brace, amplitude=5},scale=0.6, every node/.style={scale=0.6}]
	\tikzstyle{legend}=[below=0.1, anchor=mid] 	
	\node(t1) at (0,0) {};

	\node[above right=0.6cm and 0cm of t1.mid, minimum height=0.5cm, minimum width=9cm, draw=white, fill=white, scale=1.5](IMC) {$Infinite Memory Capacity$}; 	    				
	%%	    \node[above right=0.4cm and 0cm of t1.mid, minimum height=0.5cm, minimum width=9cm, draw=white, fill=white, scale=1.5](IMC) {$Infinite Memory Capacity$};

	\node[above right=0cm and 0cm of t1.mid, minimum height=0.5cm, minimum width=1cm,draw,fill=white](b11) {$B$};

	\node[below right=0cm and 0cm of b11.south east, minimum height=0.5cm, minimum width=3cm,draw,fill=white](b12) {$B$};

	\node[above right=0cm and 0cm of b11.south east, minimum height=0.5cm, minimum width=4cm,draw,fill=white](c11) {$C$};

	\node[below right=0cm and 0cm of c11.south east, minimum height=0.5cm, minimum width=4cm,draw,fill=white](c12) {$C$};

	\node[above right=0cm and 0cm of c11.south east, minimum height=0.5cm, minimum width=3cm,draw,fill=white](a11) {$A$};

	\node[below right=0cm and 0cm of c12.north east, minimum height=0.5cm, minimum width=2cm,draw,fill=white](a12) {$A$};

	\node[above right=0cm and 0cm of a11.south east, minimum height=0.5cm, minimum width=2cm,draw,fill=white](d11) {$D$};

	\node[below right=0cm and 0cm of a12.north east, minimum height=0.5cm, minimum width=1cm,draw,fill=white](d12) {$D$};

	%%		\draw[->]	(5,-1)-- (b11.west, b11.south)	;

	%%		\draw[->] ([xshift=-0.1cm, yshift=-1cm] b11.south west)--([xshift=13cm, yshift=-1cm] b11.south west);

	\draw[->] ([shift={(-0.1, -0.65)}] t1.mid)
	-- ([shift={(0, -0.65)}] t1.mid)node[legend,scale=0.65]{$0$}
	-- ([shift={(1, -0.65)}] t1.mid)node[legend,scale=0.65]{$1$}
	-- ([shift={(4, -0.65)}] t1.mid)node[legend,scale=0.65]{$4$}
	-- ([shift={(5, -0.65)}] t1.mid)node[legend,scale=0.65]{$5$}
	-- ([shift={(8, -0.65)}] t1.mid)node[legend,scale=0.65]{$8$}
	-- ([shift={(9, -0.65)}] t1.mid)node[legend,scale=0.65]{$9$}
	-- ([shift={(10, -0.65)}] t1.mid)node[legend,scale=0.65]{$10$}
	-- ([shift={(11, -0.65)}] t1.mid)node[legend,scale=0.65]{$11$}
	-- ([shift={(12, -0.65)}] t1.mid)node[legend,scale=0.65]{$12$}                                      
	--([shift={(17, -0.65)}] t1.mid)node[right,scale=0.65]{$t$};

	\foreach \x in {0, 1, 4, 5, 8, 9, 10, 11, 12} \draw ([shift={(\x, -0.61)}] t1.mid) -- ([shift={(\x, -0.69)}] t1.mid);

	\node[above left=-0.15cm and 1cm of t1.mid, scale=1, rotate=0] {$OMIM$};

	%%      \node[above right=-1.15cm and -2cm of t1.mid, scale=1, rotate=0] {$Hello BCAD$};

	\node(t1) at ([shift={(0, -3.8)}] t1.mid) {};   
	%%	    \node[above right=0cm and 0cm of t1.mid, minimum height=0.5cm, minimum width=9cm, draw=white, fill=white, scale=1.5](MC) {$Memory Capacity=6$}; 
	%%	    \node[above right=0.4cm and 0cm of t1.mid, minimum height=0.5cm, minimum width=9cm, draw=white, fill=white, scale=1.5](IMC) {$Memory Capacity=6$};	   
	\node[above right=0.6cm and 0cm of t1.mid, minimum height=0.5cm, minimum width=9cm, draw=white, fill=white, scale=1.5](IMC) {$Memory Capacity=6$};

	%%   		\node(t1) at ([shift={(0, -1.0)}] t1.mid) {};                		
	\node[above right=0cm and 0cm of t1.mid, minimum height=0.5cm, minimum width=1cm,draw,fill=white](b21) {$B$};

	\node[below right=0cm and 0cm of b21.south east, minimum height=0.5cm, minimum width=3cm,draw,fill=white](b22) {$B$};

	\node[above right=0cm and 0cm of b21.south east, minimum height=0.5cm, minimum width=4cm,draw,fill=white](c21) {$C$};

	\node[below right=0cm and 0cm of c21.south east, minimum height=0.5cm, minimum width=4cm,draw,fill=white](c22) {$C$};

	\node[above right=0cm and 0cm of c22.north east, minimum height=0.5cm, minimum width=3cm,draw,fill=white](a21) {$A$};

	\node[below right=0cm and 0cm of a21.south east, minimum height=0.5cm, minimum width=2cm,draw,fill=white](a22) {$A$};

	\node[above right=0cm and 0cm of a21.south east, minimum height=0.5cm, minimum width=2cm,draw,fill=white](d11) {$D$};

	\node[below right=0cm and 0cm of d11.south east, minimum height=0.5cm, minimum width=1cm,draw,fill=white](d12) {$D$};

	\draw[->] ([shift={(-0.1, -0.65)}] t1.mid)
	-- ([shift={(0, -0.65)}] t1.mid)node[legend,scale=0.65]{$0$}
	-- ([shift={(1, -0.65)}] t1.mid)node[legend,scale=0.65]{$1$}
	-- ([shift={(4, -0.65)}] t1.mid)node[legend,scale=0.65]{$4$}
	-- ([shift={(5, -0.65)}] t1.mid)node[legend,scale=0.65]{$5$}
	-- ([shift={(9, -0.65)}] t1.mid)node[legend,scale=0.65]{$9$}
	-- ([shift={(12, -0.65)}] t1.mid)node[legend,scale=0.65]{$12$}         
	-- ([shift={(14, -0.65)}] t1.mid)node[legend,scale=0.65]{$14$}                                      
	-- ([shift={(15, -0.65)}] t1.mid)node[legend,scale=0.65]{$15$}
	-- ([shift={(17, -0.65)}] t1.mid)node[right,scale=0.65]{$t$};

	\foreach \x in {0, 1, 4, 5, 9, 12, 14, 15} \draw ([shift={(\x, -0.61)}] t1.mid) -- ([shift={(\x, -0.69)}] t1.mid);

	\node[above left=-0.15cm and 1cm of t1.mid, scale=1, rotate=0] {$OOSIM$};

	%% schedule of third heuristic		
	\node(t1) at ([shift={(0, -1.8)}] t1.mid) {};                		
	\node[above right=0cm and 0cm of t1.mid, minimum height=0.5cm, minimum width=1cm,draw,fill=white](b31) {$B$};

	\node[below right=0cm and 0cm of b31.south east, minimum height=0.5cm, minimum width=3cm,draw,fill=white](b32) {$B$};

	\node[above right=0cm and 0cm of b31.south east, minimum height=0.5cm, minimum width=2cm,draw,fill=white](d31) {$D$};

	\node[below right=0cm and 0cm of b32.north east, minimum height=0.5cm, minimum width=1cm,draw,fill=white](d32) {$D$};

	\node[above right=0cm and 0cm of d31.south east, minimum height=0.5cm, minimum width=3cm,draw,fill=white](a31) {$A$};

	\node[below right=0cm and 0cm of a31.south east, minimum height=0.5cm, minimum width=2cm,draw,fill=white](a32) {$A$};

	\node[above right=0cm and 0cm of a32.north east, minimum height=0.5cm, minimum width=4cm,draw,fill=white](c31) {$C$};

	\node[below right=0cm and 0cm of c31.south east, minimum height=0.5cm, minimum width=4cm,draw,fill=white](c32) {$C$};

	\draw[->] ([shift={(-0.1, -0.65)}] t1.mid)
	-- ([shift={(0, -0.65)}] t1.mid)node[legend,scale=0.65]{$0$}
	-- ([shift={(1, -0.65)}] t1.mid)node[legend,scale=0.65]{$1$}
	-- ([shift={(3, -0.65)}] t1.mid)node[legend,scale=0.65]{$3$}
	-- ([shift={(4, -0.65)}] t1.mid)node[legend,scale=0.65]{$4$}
	-- ([shift={(5, -0.65)}] t1.mid)node[legend,scale=0.65]{$5$}
	-- ([shift={(6, -0.65)}] t1.mid)node[legend,scale=0.65]{$6$}         
	-- ([shift={(8, -0.65)}] t1.mid)node[legend,scale=0.65]{$8$}                                      
	-- ([shift={(12, -0.65)}] t1.mid)node[legend,scale=0.65]{$12$} 
	-- ([shift={(16, -0.65)}] t1.mid)node[legend,scale=0.65]{$16$}
	--([shift={(17, -0.65)}] t1.mid)node[right,scale=0.65]{$t$};

	\foreach \x in {0, 1, 3, 4, 5, 6, 8, 12, 16} \draw ([shift={(\x, -0.61)}] t1.mid) -- ([shift={(\x, -0.69)}] t1.mid);

	\node[above left=-0.15cm and 1cm of t1.mid, scale=1, rotate=0] {$IOCMS$};

	%% schedule of fourth heuristic		
	\node(t1) at ([shift={(0, -1.8)}] t1.mid) {};                		
	\node[above right=0cm and 0cm of t1.mid, minimum height=0.5cm, minimum width=4cm,draw,fill=white](c41) {$C$};

	\node[below right=0cm and 0cm of c41.south east, minimum height=0.5cm, minimum width=4cm,draw,fill=white](c42) {$C$};

	\node[above right=0cm and 0cm of c41.south east, minimum height=0.5cm, minimum width=1cm,draw,fill=white](b41) {$B$};

	\node[below right=0cm and 0cm of c42.north east, minimum height=0.5cm, minimum width=3cm,draw,fill=white](b42) {$B$};

	\node[above right=0cm and 0cm of c42.north east, minimum height=0.5cm, minimum width=3cm,draw,fill=white](a41) {$A$};

	\node[below right=0cm and 0cm of a41.south east, minimum height=0.5cm, minimum width=2cm,draw,fill=white](a42) {$A$};

	\node[above right=0cm and 0cm of b42.north east, minimum height=0.5cm, minimum width=2cm,draw,fill=white](d41) {$D$};

	\node[below right=0cm and 0cm of d41.south east, minimum height=0.5cm, minimum width=1cm,draw,fill=white](d42) {$D$};

	\draw[->] ([shift={(-0.1, -0.65)}] t1.mid)
	-- ([shift={(0, -0.65)}] t1.mid)node[legend,scale=0.65]{$0$}
	-- ([shift={(4, -0.65)}] t1.mid)node[legend,scale=0.65]{$4$}
	-- ([shift={(5, -0.65)}] t1.mid)node[legend,scale=0.65]{$5$}
	-- ([shift={(8, -0.65)}] t1.mid)node[legend,scale=0.65]{$8$}
	-- ([shift={(11, -0.65)}] t1.mid)node[legend,scale=0.65]{$11$}
	-- ([shift={(13, -0.65)}] t1.mid)node[legend,scale=0.65]{$13$}         
	-- ([shift={(14, -0.65)}] t1.mid)node[legend,scale=0.65]{$14$} 
	--([shift={(17, -0.65)}] t1.mid)node[right,scale=0.65]{$t$};

	\foreach \x in {0, 4, 5, 8, 11, 13, 14} \draw ([shift={(\x, -0.61)}] t1.mid) -- ([shift={(\x, -0.69)}] t1.mid);

	\node[above left=-0.15cm and 1cm of t1.mid, scale=1, rotate=0] {$DOCPS$};

	%% schedule of fifth heuristic		
	\node(t1) at ([shift={(0, -1.8)}] t1.mid) {};                		
	\node[above right=0cm and 0cm of t1.mid, minimum height=0.5cm, minimum width=2cm,draw,fill=white](d51) {$D$};

	\node[below right=0cm and 0cm of d51.south east, minimum height=0.5cm, minimum width=1cm,draw,fill=white](d52) {$D$};

	\node[above right=0cm and 0cm of d51.south east, minimum height=0.5cm, minimum width=1cm,draw,fill=white](b51) {$B$};

	\node[below right=0cm and 0cm of b51.south east, minimum height=0.5cm, minimum width=3cm,draw,fill=white](b52) {$B$};

	\node[above right=0cm and 0cm of d52.north east, minimum height=0.5cm, minimum width=3cm,draw,fill=white](a51) {$A$};

	\node[below right=0cm and 0cm of a51.south east, minimum height=0.5cm, minimum width=2cm,draw,fill=white](a52) {$A$};

	\node[above right=0cm and 0cm of a52.north east, minimum height=0.5cm, minimum width=4cm,draw,fill=white](c51) {$C$};

	\node[below right=0cm and 0cm of c51.south east, minimum height=0.5cm, minimum width=4cm,draw,fill=white](c52) {$C$};

	\draw[->] ([shift={(-0.1, -0.65)}] t1.mid)
	-- ([shift={(0, -0.65)}] t1.mid)node[legend,scale=0.65]{$0$}
	-- ([shift={(2, -0.65)}] t1.mid)node[legend,scale=0.65]{$2$}
	-- ([shift={(3, -0.65)}] t1.mid)node[legend,scale=0.65]{$3$}
	-- ([shift={(6, -0.65)}] t1.mid)node[legend,scale=0.65]{$6$}
	-- ([shift={(8, -0.65)}] t1.mid)node[legend,scale=0.65]{$8$}
	-- ([shift={(12, -0.65)}] t1.mid)node[legend,scale=0.65]{$12$}         
	-- ([shift={(16, -0.65)}] t1.mid)node[legend,scale=0.65]{$16$} 
	--([shift={(17, -0.65)}] t1.mid)node[right,scale=0.65]{$t$};

	\foreach \x in {0, 2, 3, 6, 8, 12, 16} \draw ([shift={(\x, -0.61)}] t1.mid) -- ([shift={(\x, -0.69)}] t1.mid);

	\node[above left=-0.15cm and 1cm of t1.mid, scale=1, rotate=0] {$IOCCS$};

	%% schedule of sixth heuristic		
	\node(t1) at ([shift={(0, -1.8)}] t1.mid) {};                		
	\node[above right=0cm and 0cm of t1.mid, minimum height=0.5cm, minimum width=4cm,draw,fill=white](c61) {$C$};

	\node[below right=0cm and 0cm of c61.south east, minimum height=0.5cm, minimum width=4cm,draw,fill=white](c62) {$C$};

	\node[above right=0cm and 0cm of c62.north east, minimum height=0.5cm, minimum width=3cm,draw,fill=white](a61) {$A$};

	\node[below right=0cm and 0cm of a61.south east, minimum height=0.5cm, minimum width=2cm,draw,fill=white](a62) {$A$};

	\node[above right=0cm and 0cm of a61.south east, minimum height=0.5cm, minimum width=1cm,draw,fill=white](b61) {$B$};

	\node[below right=0cm and 0cm of a62.north east, minimum height=0.5cm, minimum width=3cm,draw,fill=white](b62) {$B$};

	\node[above right=0cm and 0cm of b61.south east, minimum height=0.5cm, minimum width=2cm,draw,fill=white](d61) {$D$};

	\node[below right=0cm and 0cm of b62.north east, minimum height=0.5cm, minimum width=1cm,draw,fill=white](d62) {$D$};

	\draw[->] ([shift={(-0.1, -0.65)}] t1.mid)
	-- ([shift={(0, -0.65)}] t1.mid)node[legend,scale=0.65]{$0$}
	-- ([shift={(4, -0.65)}] t1.mid)node[legend,scale=0.65]{$4$}
	-- ([shift={(8, -0.65)}] t1.mid)node[legend,scale=0.65]{$8$}
	-- ([shift={(11, -0.65)}] t1.mid)node[legend,scale=0.65]{$11$}
	-- ([shift={(12, -0.65)}] t1.mid)node[legend,scale=0.65]{$12$}
	-- ([shift={(13, -0.65)}] t1.mid)node[legend,scale=0.65]{$13$}         
	-- ([shift={(14, -0.65)}] t1.mid)node[legend,scale=0.65]{$14$}
	-- ([shift={(16, -0.65)}] t1.mid)node[legend,scale=0.65]{$16$} 
	-- ([shift={(17, -0.65)}] t1.mid)node[legend,scale=0.65]{$17$}  
	--([shift={(17.1, -0.65)}] t1.mid)node[right,scale=0.65]{$t$};

	\foreach \x in {0, 4, 8, 11, 12, 13, 14, 16, 17} \draw ([shift={(\x, -0.61)}] t1.mid) -- ([shift={(\x, -0.69)}] t1.mid);

	\node[above left=-0.15cm and 1cm of t1.mid, scale=1, rotate=0] {$DOCCS$};

	%%  \draw ([yshift=-0.5mm] second0.north)
	%%		-- ([yshift=-0.5mm, xshift=0.5mm] second0.north)
	%%		-- ([xshift=0.5mm] second0.north);

	%%		\node[above left=0.15cm and 0cm of t2.south west, scale=0.5, rotate=0] {$GPU$};
	%%		\node[above left=0.15cm and 0cm of t3.south west, scale=0.5, rotate=0] {$CPU$};		
	%%		
	%%		\tikzstyle{legend}=[below=0.35, anchor=mid] 	
	%%		\draw[->] (-0.1, -0.1) -- (0, -0.1)  node[legend,scale=0.65]{$0$} --(1,-0.1) node [legend,scale=0.65]{$1$} --(1.5, -0.1) node[right,scale=0.65]{$t$}; 
	%%		
	%%		\foreach \x in {0cm, 1cm} \draw (\x, -0.12) -- (\x, -0.08);
	%%		%%			To align both figures of subfloat-- an object without drawing at the same depth
	%%		\path (-0.1, -0.5) -- (1.5, -0.5);

	\end{tikzpicture}

	\caption{ \label{fig:staticOrderExample} Different static order heuristic schedules for Table~\ref{tab:staticOrderExample}.}
\end{figure}

@@

\begin{figure}[htb]
	\centering
	%% 	\subfloat[Optimal schedule]{
	\begin{tikzpicture}[decoration={brace, amplitude=5},scale=0.6, every node/.style={scale=0.6}]
	\tikzstyle{legend}=[below=0.1, anchor=mid] 	
	\node(t1) at (0,0) {};  
	\node[above right=0.6cm and 0cm of t1.mid, minimum height=0.5cm, minimum width=15cm, draw=white, fill=white, scale=1.5](IMC) {$Memory Capacity=6$};

	\node[above right=0cm and 0cm of t1.mid, minimum height=0.5cm, minimum width=1cm,draw,fill=white](b11) {$B$};

	\node[below right=0cm and 0cm of b11.south east, minimum height=0.5cm, minimum width=6cm,draw,fill=white](b12) {$B$};

	\node[above right=0cm and 0cm of b11.south east, minimum height=0.5cm, minimum width=5cm,draw,fill=white](d11) {$D$};

	\node[below right=0cm and 0cm of b12.north east, minimum height=0.5cm, minimum width=1cm,draw,fill=white](d12) {$D$};

	\node[above right=0cm and 0cm of d12.north east, minimum height=0.5cm, minimum width=3cm,draw,fill=white](a11) {$A$};

	\node[below right=0cm and 0cm of a11.south east, minimum height=0.5cm, minimum width=2cm,draw,fill=white](a12) {$A$};

	\node[above right=0cm and 0cm of a12.north east, minimum height=0.5cm, minimum width=4cm,draw,fill=white](c11) {$C$};

	\node[below right=0cm and 0cm of c11.south east, minimum height=0.5cm, minimum width=6cm,draw,fill=white](c12) {$C$};

	\draw[->] ([shift={(-0.1, -0.65)}] t1.mid)
	-- ([shift={(0, -0.65)}] t1.mid)node[legend,scale=0.65]{$0$}
	-- ([shift={(1, -0.65)}] t1.mid)node[legend,scale=0.65]{$1$}
	-- ([shift={(6, -0.65)}] t1.mid)node[legend,scale=0.65]{$6$}
	-- ([shift={(7, -0.65)}] t1.mid)node[legend,scale=0.65]{$7$}
	-- ([shift={(8, -0.65)}] t1.mid)node[legend,scale=0.65]{$8$}
	-- ([shift={(11, -0.65)}] t1.mid)node[legend,scale=0.65]{$11$}         
	-- ([shift={(13, -0.65)}] t1.mid)node[legend,scale=0.65]{$13$}                                      
	-- ([shift={(17, -0.65)}] t1.mid)node[legend,scale=0.65]{$17$}
	-- ([shift={(23, -0.65)}] t1.mid)node[legend,scale=0.65]{$23$}
	-- ([shift={(25.1, -0.65)}] t1.mid)node[right,scale=0.65]{$t$};

	\foreach \x in {0, 1, 6, 7, 8, 11, 13, 17, 23} \draw ([shift={(\x, -0.61)}] t1.mid) -- ([shift={(\x, -0.69)}] t1.mid);

	\node[above left=-0.15cm and 1cm of t1.mid, scale=1, rotate=0] {$LCMR$};

	%% schedule of third heuristic		
	\node(t1) at ([shift={(0, -1.8)}] t1.mid) {};                		
	\node[above right=0cm and 0cm of t1.mid, minimum height=0.5cm, minimum width=1cm,draw,fill=white](b21) {$B$};

	\node[below right=0cm and 0cm of b21.south east, minimum height=0.5cm, minimum width=6cm,draw,fill=white](b22) {$B$};

	\node[above right=0cm and 0cm of b21.south east, minimum height=0.5cm, minimum width=3cm,draw,fill=white](a21) {$A$};

	\node[below right=0cm and 0cm of b22.north east, minimum height=0.5cm, minimum width=2cm,draw,fill=white](a22) {$A$};

	\node[above right=0cm and 0cm of a22.north east, minimum height=0.5cm, minimum width=4cm,draw,fill=white](c21) {$C$};

	\node[below right=0cm and 0cm of c21.south east, minimum height=0.5cm, minimum width=6cm,draw,fill=white](c22) {$C$};

	\node[above right=0cm and 0cm of c22.north east, minimum height=0.5cm, minimum width=5cm,draw,fill=white](d21) {$D$};

	\node[below right=0cm and 0cm of d21.south east, minimum height=0.5cm, minimum width=1cm,draw,fill=white](d22) {$D$};

	\draw[->] ([shift={(-0.1, -0.65)}] t1.mid)
	-- ([shift={(0, -0.65)}] t1.mid)node[legend,scale=0.65]{$0$}
	-- ([shift={(1, -0.65)}] t1.mid)node[legend,scale=0.65]{$1$}
	-- ([shift={(4, -0.65)}] t1.mid)node[legend,scale=0.65]{$4$}
	-- ([shift={(7, -0.65)}] t1.mid)node[legend,scale=0.65]{$7$}
	-- ([shift={(9, -0.65)}] t1.mid)node[legend,scale=0.65]{$9$}
	-- ([shift={(13, -0.65)}] t1.mid)node[legend,scale=0.65]{$13$}         
	-- ([shift={(19, -0.65)}] t1.mid)node[legend,scale=0.65]{$19$}                                      
	-- ([shift={(24, -0.65)}] t1.mid)node[legend,scale=0.65]{$24$}
	-- ([shift={(25, -0.65)}] t1.mid)node[legend,scale=0.65]{$25$}
	-- ([shift={(25.1, -0.65)}] t1.mid)node[right,scale=0.65]{$t$};

	\foreach \x in {0, 1, 4, 7, 9, 13, 19, 24, 25} \draw ([shift={(\x, -0.61)}] t1.mid) -- ([shift={(\x, -0.69)}] t1.mid);

	\node[above left=-0.15cm and 1cm of t1.mid, scale=1, rotate=0] {$SCMR$};

	%% schedule of third heuristic		
	\node(t1) at ([shift={(0, -1.8)}] t1.mid) {};    	
	\node[above right=0cm and 0cm of t1.mid, minimum height=0.5cm, minimum width=1cm,draw,fill=white](b31) {$B$};

	\node[below right=0cm and 0cm of b31.south east, minimum height=0.5cm, minimum width=6cm,draw,fill=white](b32) {$B$};

	\node[above right=0cm and 0cm of b31.south east, minimum height=0.5cm, minimum width=4cm,draw,fill=white](c31) {$C$};

	\node[below right=0cm and 0cm of b32.north east, minimum height=0.5cm, minimum width=6cm,draw,fill=white](c32) {$C$};

	\node[above right=0cm and 0cm of c32.north east, minimum height=0.5cm, minimum width=3cm,draw,fill=white](a31) {$A$};

	\node[below right=0cm and 0cm of a31.south east, minimum height=0.5cm, minimum width=2cm,draw,fill=white](a32) {$A$};

	\node[above right=0cm and 0cm of a32.north east, minimum height=0.5cm, minimum width=5cm,draw,fill=white](d31) {$D$};

	\node[below right=0cm and 0cm of d31.south east, minimum height=0.5cm, minimum width=1cm,draw,fill=white](d32) {$D$};

>>>>

	\begin{algorithm}
		\caption{\label{alg:OrderOfExecutionInfinteMemory}Algorithm to determine the order of processing and schedule for a set of ready tasks (infinite memory case)}
		\begin{algorithmic}[1]
			\STATE Divide ready tasks in two sets $S_1$ and $S_2$. If computation time of a task $T$is not less than its communication time, then $T$ is in $S_1$ otherwise in $S_2$.
			\STATE Sort $S_1$ in queue $Q$ by non-decreasing communication times
			\STATE Sort $S_2$ in queue $Q'$ by non-increasing computation times
			\STATE Append $Q'$ to $Q$
			\STATE $early\_available\_time\_on\_communication\_resource \gets 0$
			\STATE $early\_available\_time\_on\_computation\_resource \gets 0$
			\WHILE{$Q \neq \emptyset$}
			\STATE remove a task $T$ from beginning of $Q$ for processing
			\STATE $\scomm(T) \gets  early\_available\_time\_on\_communication\_resource$
			\STATE $\scomp(T) \gets  max(\scomm(T) + CM_T, early\_available\_time\_on\_computation\_resource)$
			\STATE $early\_available\_time\_on\_communication\_resource \gets  \scomm(T) + CM_T$
			\STATE $early\_available\_time\_on\_computation\_resource \gets  \scomp(T) + CP_T$
			\ENDWHILE
		\end{algorithmic}
	\end{algorithm}

@@

		\begin{figure}[htb]
			\tikzset{xtick/.style={inner xsep=0pt, inner ysep=3pt, minimum
					size=0pt, draw},%
				task/.style args={#1start#2length#3res#4color#5}{rounded corners, draw, inner
					sep=0pt, fill=#5, label=center:#1, fit={(#2,#4*0.75)
						(#2+#3,#4*0.75+0.75)}},%
				vert/.style={inner sep=1pt, fill=black, circle, draw, label=#1}
			}
			\newcommand{\schedule}[1]{
				\draw[->] (-0.4, 0) -- (#1, 0) node[below] {$t$};
				\draw     (0, 0)    -- (0, 1.5) node[pos=0.25, left] {Compute}
				node[pos=0.75, left] {Comm.};
				\draw[dashed,gray] (0, 0.75) -- (#1, 0.75);
			}
			\centering
			\begin{tikzpicture}[scale=0.7, thick]
			\schedule{9.5}
			\node[task=$A_{i1}$ start 0 length 1 res 1 color cyan]{};
			\node[task=$A_{i2}$ start 1 length 1 res 1 color blue!70!white]{};
			\node[task=$A_{i3}$ start 2 length 1 res 1 color blue]{};
			\node[task=$K_0$   start 0 length 3 res 0 color gray!40!white]{};
			\node[task=$K_1$  start 3 length 6 res 1 color green]{}; 
			\node[task=$A_{i1}$ start 3 length 1.8 res 0 color cyan]{};
			\node[task=$A_{i2}$ start 4.8 length 2.3 res 0 color blue!70!white]{};
			\node[task=$A_{i3}$ start 7.1 length 1.9 res 0 color blue]{};
			\draw[<->,thin] (0, -0.2) -- node[below]{$3$} (3, -0.2) ;
			\draw[<->,thin] (3, -0.2) -- node[below]{$b'$} (9, -0.2) ;
			\end{tikzpicture}
			\caption{ \label{fig:firstSegment} First segment of Schedule $S$.}
		\end{figure}

@@

	\tikzset{xtick/.style={inner xsep=0pt, inner ysep=3pt, minimum
			size=0pt, draw, label=below:#1},%
		comm/.style args={#1start#2length#3color#4}{rounded corners=1mm, draw, inner
			sep=0pt, fill=#4, label=center:#1, fit={(#2,0.75)
				(#2+#3,1.5)}},%
		comp/.style args={#1start#2length#3color#4}{rounded corners=1mm, draw, inner
			sep=0pt, fill=#4, label=center:#1, fit={(#2,0)
				(#2+#3,0.75)}},%
	}
	\newcommand{\schedule}[3]{
		\draw[->] (-0.2, 0) -- (#1, 0) node[below] {$t$};
		\draw     (0, 0)    -- (0, 1.5);
		\node at (-0.8, 0.75)[rotate=90] {#2};
		\draw[dashed,gray] (0, 0.75) -- (#1, 0.75);
		\foreach \t in {0,#3} {
			\node[xtick=\t] at (\t, 0){};
		}
	}
	\newcommand{\task}[6][0]{
		\node[comm=#2 start #3 length #4 color #6]{};
		\node[comp=#2 start #3+#4+#1 length #5 color #6]{}; 
	}

	\begin{figure}[htb]
		\newcommand{\taskA}[2][0]{\task[#1]{$A$}{#2}{3}{2}{cyan}}
		\newcommand{\taskB}[2][0]{\task[#1]{$B$}{#2}{1}{3}{blue!40!white}}
		\newcommand{\taskC}[2][0]{\task[#1]{$C$}{#2}{4}{4}{blue!70!white}}
		\newcommand{\taskD}[2][0]{\task[#1]{$D$}{#2}{2}{1}{blue}}

		\centering
		\subfloat[][Infinite Memory Capacity]{
			\begin{tikzpicture}[scale=0.6]
			\schedule{12.5}{OMIM}{1,4,5,8,9,10,11,12}
			\taskB{0}
			\taskC{1}
			\taskA[1]{5}
			\taskD[1]{8}
			\end{tikzpicture}
		}

		\subfloat[][Memory Capacity: 6]{
			\begin{tikzpicture}[yscale=0.6, xscale=0.45]
			\begin{scope}
			\schedule{15.5}{OOSIM}{1,4,5,9,12,14,15}
			\taskB{0}
			\taskC{1}
			\taskA{9}
			\taskD{12}
			\end{scope}
			\begin{scope}[yshift=-2.75cm]
			\schedule{16.5}{IOCMS}{1,3,4,5,6,8,12,16}
			\taskB{0}
			\taskD[1]{1}
			\taskA{3}
			\taskC{8}
			\end{scope}
			\begin{scope}[yshift=-5.5cm]
			\schedule{14.5}{DOCPS}{4,5,8,11,13,14}
			\taskC{0}
			\taskB[3]{4}
			\taskA{8}
			\taskD{11}
			\end{scope}
			\begin{scope}[yshift=-8.25cm]
			\schedule{16.5}{IOCCS}{2,3,6,8,12,16}
			\taskD{0}
			\taskB{2}
			\taskA{3}
			\taskC{8}
			\end{scope}
			\begin{scope}[yshift=-11cm]
			\schedule{17.5}{DOCCS}{4,8,11,12,13,14,16,17}
			\taskC{0}
			\taskA{8}
			\taskB[1]{11}
			\taskD[2]{12}
			\end{scope}
			\end{tikzpicture}
		}

		\caption{ \label{fig:staticOrderExample} Different static
			order heuristic schedules for
			Table~\ref{tab:staticOrderExample}. Optimal schedule length
			is 14. }
	\end{figure}

@@

	\begin{figure}[htb]
		\centering

		\newcommand{\taskA}[2][0]{\task[#1]{$A$}{#2}{3}{2}{cyan}}
		\newcommand{\taskB}[2][0]{\task[#1]{$B$}{#2}{1}{6}{blue!40!white}}
		\newcommand{\taskC}[2][0]{\task[#1]{$C$}{#2}{4}{6}{blue!70!white}}
		\newcommand{\taskD}[2][0]{\task[#1]{$D$}{#2}{5}{1}{blue}}

		\centering
		\begin{tikzpicture}[yscale=0.6,xscale=0.3]
		\begin{scope}
		\schedule{24}{LCMR}{1,6,7,8,11,13,17,23}
		\taskB{0}
		\taskD[1]{1}
		\taskA{8}
		\taskC{13}
		\end{scope}
		\begin{scope}[yshift=-2.75cm]
		\schedule{26}{SCMR}{1,4,7,9,13,19,24,25}
		\taskB{0}
		\taskA[3]{1}
		\taskC{9}
		\taskD{19}
		\end{scope}
		\begin{scope}[yshift=-5.5cm]
		\schedule{25}{MAMR}{1,5,7,13,16,18,23,24}
		\taskB{0}
		\taskC[2]{1}
		\taskA{13}
		\taskD{18}
		\end{scope}
		\end{tikzpicture}
		\caption{ \label{fig:dynamicSelectionExample} Different dynamic heuristic schedules for a task set of Table~\ref{tab:dynamicSelectionExample} for a memory capacity of 6. Optimal schedule length is 23.}
	\end{figure}
